\EVOSUITE at the SBST 2018 Tool Competition

### 2018-03-16 papers/sbst18/paper_sbst18.tex
Add ACM copyright
Update Andreas affiliation, and typo

@@

\author{Andrea Arcuri}
\affiliation{%
  \institution{Westerdals Oslo ACT}
  \city{Oslo}
  \country{Norway}
}
\email{arcand@westerdals.no}

@@

Amongst those benchmarks for which
\EVOSUITE struggled with flakiness, FASTJSON-4 is a notable example:
in the worst case, 90 flaky tests were generated in one single run. An
analysis of the execution logs indicates several possible sources for
this flakiness: a) a non-final static constant that is not properly
reset in between executions; b) an possibly incorrect handling of enum
types; and c) a global property not being reset in between
executions. Considering that there were still remaining flaky tests, further investigation will be needed to confirm these
conjectures and act upon them.

@@

%\noindent
\textbf{Acknowledgments:} Many thanks to all the contributors to \EVOSUITE.
This project has been funded by the EPSRC
project ``GREATEST'' (EP/N023978/1).
%, and by the National Research
%Fund, Luxembourg (FNR/P10/03)\TODO{remove?}.

>>>>

\copyrightyear{2018} 
\acmYear{2018} 
\setcopyright{acmcopyright}
\acmConference[SBST'18]{SBST'18:IEEE/ACM 11th International Workshop on Search-Based Software Testing }{May 28--29, 2018}{Gothenburg, Sweden}
\acmBooktitle{SBST'18: SBST'18:IEEE/ACM 11th International Workshop on Search-Based Software Testing , May 28--29, 2018, Gothenburg, Sweden}
\acmPrice{15.00}
\acmDOI{10.1145/3194718.3194729}
\acmISBN{978-1-4503-5741-8/18/05}

@@

\author{Andrea Arcuri}
\affiliation{%
  \institution{Westerdals Oslo ACT, Norway  and University of
    Luxembourg, Luxembourg}
%  \city{Oslo}
%  \country{Norway}
}
\email{arcand@westerdals.no}

@@

Amongst those benchmarks for which
\EVOSUITE struggled with flakiness, FASTJSON-4 is a notable example:
in the worst case, 90 flaky tests were generated in one single run. An
analysis of the execution logs indicates several possible sources for
this flakiness: a) a non-final static constant that is not properly
reset in between executions; b) a possibly incorrect handling of enum
types; and c) a global property not being reset in between
executions. Considering that there were still remaining flaky tests, further investigation will be needed to confirm these
conjectures and act upon them.

@@

%\noindent
\textbf{Acknowledgments:} Many thanks to all the contributors to
\EVOSUITE.  This project has been funded by the EPSRC project
``GREATEST'' (EP/N023978/1), and by the National Research Fund,
Luxembourg (FNR/P10/03).
